One-dimensional turbulence (ODT): computationally efficient modeling and simulation of turbulent flows

### 2020-11-12 submissions/response_to_reviews_1.md

    -   YAML: specify the name of the needed yaml package is: yaml-cpp

    ***We made this clarification in section 2.3.1 as requested.***

-   Input files: Consider adding a feature that helps to specify the
    dumpTimes. For example, add the capability to parse the following
    values (Start, End, Step ) from the input file rather than
    specifying all the times you want to save the data manually.

    ***We have now included this feature as requested. The user can specify times either through the original dumpTimes key, or through a new dumpTimesGen key that includes start, stop, and step variables. If both are present in the input file dumpTimesGen takes precedence, unless a negative start time is specified. This is demonstrated in the newly modified input file for the channel flow case, with comments to note the behavior and usage. We have also edited the paper and code documentation appropriately.***

@@

-   Running ODT:

    -   The running interface is not trivial and limits the user to a
        predefined data storage location.This may cause problems for
        some users.

    -   My recommendation is to put all these run scripts under a single
        python interface that will allow the user to select the number
        of realization, the number of processes (when running in
        parallel), the input file, \... .

@@

        -   consider using python classes for the interface, it will
            make you code much cleaner

        -   check argparse module in python!

    ***We have carefully considered the reviewer's suggestion. The running of the code falls into two broad categories: running smaller simulations on a desktop computer, and running larger parallel simulations on Linux clusters. The scripts that we have provided are well-documented, and we have also provided a video going through the process. In addition, many of our current users are used to the existing interface, and changing this might cause confusion. For single desktop jobs, the runOneRlz.sh script is easy to use, with two variables for the user to edit at the top. For parallel jobs, users will be familiar with scripts using job submission software (e.g., slurm), and examples are provided that can be edited. We will keep this option open.***

@@

-   Data files and Post-processing:

    -   In the paper, you mentioned in line 118 that the package
        contains auxiliary data processing and visualization tools.
        However, later in section 2.3.4 Data files and post-processing
        you mentioned in line 237 that those tools are organized by case
        type meaning that these post-processing tools are specific for
        the input files provided as examples. This may cause confusion
        to the user.

        ***The reference on line 118 is a short note that post-processing tools are provided. The description in section 2.3.4 is more detailed and provides a more complete description. We certainly want to avoid confusion. We have edited the comment on line 118 to note that the post-processing tools are specific to the case, and include a pointer to the later discussion.***

@@

    -   Also, you didn't mention the tools you provided that help the
        user load the data. (ODT/Post/tools)

        ***This is a good comment. We have added a paragraph to the end of section 2.3.4 that describes these tools.***

@@

        -   I recommend that you put these functions under a python
            class that takes as a value the path to the data you saved.
            This will give flexibility to the user to load any data
            stored on his local or remote machines.

            ***This is a valid suggestion for implementation, and is very similar to the approach that we have chosen. Namely, the functions are in a python module and can be easily accessed by importing the module. Many of these functions take a single dictionary argument that provides the case name as well as relevant paths (e.g., to the data or post directories of the given case). This dictionary is build in the driver script based on the user-supplied case name. We have explaned this in the new paragraph in section 2.3.4 noted above.***

        -   Describe those functions in the paper.
        <br>
        ***Done, as requested.***

### 2020-11-12 submissions/differences_initial_vs_revision_1/manuscript.tex
revision submitted to journal, adding differences between original and revision.

@@

Transport equations for mass, momentum, and enthalpy in the temporal formulation of ODT take the following generic form, derived from the Reynolds Transport Theorem~\cite{Cengel_2010} for a given scalar quantity per unit mass $\beta$: 
\begin{equation} 
\label{eq:transport}
	\frac{\mathrm{d}\beta}{\mathrm{d}t} = -\frac{j_{\beta,e}A_{x,e}-j_{\beta,w}A_{x,w}}{\rho V} + \frac{S_{\beta}}{\rho V}.
\end{equation}
The first and second terms on the right-hand-side of this equation are the diffusive transport and source terms, respectively. Here, the term \emph{diffusive} is not specific to mass transfer, but may refer to the transport of, e.g., heat, mass, and momentum, depending on the identity of the scalar $\beta$. In practice, we refer to the transport term as the ``mixing term`. The symbols shown in Equation~\ref{eq:transport} are defined as follows: $j_{\beta}$ is the diffusion flux of scalar $\beta$ across the cell face area $A_x$, where the subscripts $e$ and $w$ refer to the ``east" and ``west" faces of a given grid cell, respectively; $S_{\beta}$ is the Lagrangian source term derived from the conservation law for $\beta$; $\rho$ represents mass density; and $V$ represents cell volume. The generic transport equation differs slightly in the spatial formulation of ODT, but its form is similar, so we omit it here for brevity. The system of ordinary differential equations (ODEs) that results is well behaved at all grid points and in all geometries in their finite-volume forms. For details on transport equation derivation and use in both the temporal and spatial formulations of ODT, see~\cite{Lignell_2018}.

@@

Eddy events occur concurrently with diffusive advancement via solution of the system of unsteady one-dimensional transport equations. In this way, the ODT code marches in time or space until it reaches the simulation end point. Due to the stochastic nature of eddy events, each ODT simulation, or realization, is different, even when it is provided with the same input parameters. In order to obtain statistically stable data for a given set of parameters, we run many realizations with the same input parameters and then gather statistics over these realizations. This is done via post-processing tools, which are provided in the ODT package.

@@

The \texttt{yaml-cpp} package is required in order to process input files. If it has not yet been installed, it must be built and installed at this point. For convenience, the ODT package automates this process. YAML need only be installed once for a given instance of the ODT package. Rebuilding the ODT code with CMake does not affect the YAML installation.

@@

\subsubsection{Data files and post-processing}

@@

\begin{figure}
	\centering
    \includegraphics[width=\textwidth]{fig_data_folder_structure.pdf} 
	\caption{Data folder structure and file locations. Boxes indicate folders and ovals indicate files. For a given simulation, \texttt{caseName} will be replaced with the case name specified in the run script. The number attached to \texttt{caseName} folder names and to \texttt{runtime} data files indicates the realization number. The number attached to \texttt{dmp} files indicates the index of the list of ``dump" times included in, or generated from the information in \texttt{input.yaml}.}
\label{fig:data_folder_structure}
\end{figure}

To use post-processing tools, users navigate to the \texttt{post} directory. Within the \texttt{post} directory, data processing tools are organized by case type, which is specified in \texttt{input.yaml} and determines case-specific variables and simulation setup parameters (refer to the \texttt{domaincase} object in Figure \ref{fig:flowchart}). Each set of post-processing tools is different, but may contain some combination of Jupyter notebooks, Python scripts (often coordinated by a \texttt{driver.py} file), experimental data files for comparison and plot generation, or other supplementary files. Post-processed data and generated plots are deposited in the \texttt{data} directory, within the appropriate \texttt{caseName/post} folder.

@@

This work was supported in part by the National Science Foundation under Grant No. CBET-1403403.
%TODO, we probably need to add some acknowlegements here for those who contributed to the code.

%Special thanks to Alan R. Kerstein for his significant contributions to model development. Additional thanks to Heiko Schmidt, Juan Medina, and Marten Klein of Brandenburg University of Technology Cottbus-Senftenberg, Michael Oevermann and Marco Fistler of Chalmers University of Technology, and Vladimir P. Solovjov of Brigham Young University.

>>>>

\usepackage{soul}
\usepackage{color}

@@

Transport equations for mass, momentum, and enthalpy in the temporal formulation of ODT take the following generic form, derived from the Reynolds Transport Theorem~\cite{Cengel_2010} for a given scalar quantity per unit mass $\beta$: 
\begin{equation} 
\label{eq:transport}
	\frac{\mathrm{d}\beta}{\mathrm{d}t} = -\frac{j_{\beta,e}A_{x,e}-j_{\beta,w}A_{x,w}}{\rho V} + \frac{S_{\beta}}{\rho V}.
\end{equation}
\hl{The first and second terms on the right-hand-side of this equation are the diffusive transport and source terms, respectively. Here, the term \emph{diffusive} is not specific to mass transfer, but may refer to the transport of, e.g., heat, mass, and momentum, depending on the identity of the scalar $\beta$. In practice, we refer to the transport term as the ``mixing term`. The symbols shown in} Equation~\ref{eq:transport} \hl{are defined as follows: $j_{\beta}$ is the diffusion flux of scalar $\beta$ across the cell face area $A_x$, where the subscripts $e$ and $w$ refer to the ``east" and ``west" faces of a given grid cell, respectively; $S_{\beta}$ is the Lagrangian source term derived from the conservation law for $\beta$; $\rho$ represents mass density; and $V$ represents cell volume.} The generic transport equation differs slightly in the spatial formulation of ODT, but its form is similar, so we omit it here for brevity. The system of ordinary differential equations (ODEs) that results is well behaved at all grid points and in all geometries in their finite-volume forms. For details on transport equation derivation and use in both the temporal and spatial formulations of ODT, see~\cite{Lignell_2018}.

@@

Eddy events occur concurrently with diffusive advancement via solution of the system of unsteady one-dimensional transport equations. In this way, the ODT code marches in time or space until it reaches the simulation end point. Due to the stochastic nature of eddy events, each ODT simulation, or realization, is different, even when it is provided with the same input parameters. In order to obtain statistically stable data for a given set of parameters, we run many realizations with the same input parameters and then gather statistics over these realizations. This is done via post-processing tools. \hl{Post-processing is specific to a given case and the needs of the user. Examples of post-processing files are included for different cases provided with the ODT code, as discussed further in Section}~\ref{sec:data_files_post_processing}.

@@

\hl{The \texttt{yaml-cpp} package} is required in order to process input files. If it has not yet been installed, it must be built and installed at this point. For convenience, the ODT package automates this process. YAML need only be installed once for a given instance of the ODT package. Rebuilding the ODT code with CMake does not affect the YAML installation.

@@

\subsubsection{Data files and post-processing}
\label{sec:data_files_post_processing}

@@

\begin{figure}
	\centering
    \includegraphics[width=\textwidth]{fig_data_folder_structure.pdf} 
    \caption{Data folder structure and file locations. Boxes indicate folders and ovals indicate files. For a given simulation, \texttt{caseName} will be replaced with the case name specified in the run script. The number attached to \texttt{caseName} folder names and to \texttt{runtime} data files indicates the realization number. The number attached to \texttt{dmp} files indicates the \hl{index of the list of ``dump" times included in, or generated from the information} in \texttt{input.yaml}.}
\label{fig:data_folder_structure}
\end{figure}

To use post-processing tools, users navigate to the \texttt{post} directory. Within the \texttt{post} directory, data processing tools are organized by case type, which is specified in \texttt{input.yaml} and determines case-specific variables and simulation setup parameters (refer to the \texttt{domaincase} object in Figure \ref{fig:flowchart}). Each set of post-processing tools is different, but may contain some combination of \hl{Jupyter notebooks,} Python scripts (often coordinated by a \texttt{driver.py} file), experimental data files for comparison and plot generation, or other supplementary files. Post-processed data and generated plots are deposited in the \texttt{data} directory, within the appropriate \texttt{caseName/post} folder.

\hl{As part of the post-processing tools, there is a \texttt{post/tools} directory that contains two files: \texttt{data\_py.py} and \texttt{data\_tools.py}. The first of these can be used to convert the text data files generated during a run into binary numpy files. This can reduce both the number of data files and the file sizes. The number of files is reduced since all code realizations at a given output time are saved in the same binary file. The \texttt{data\_tools.py} file is a module that contains a number of functions for processing the data files, such as functions to}
%
\begin{itemize}
    \item \hl{get the data from a given realization,}
    \item \hl{return the number of realizations,}
    \item \hl{get a list of the variable names in the data files,}
    \item \hl{compute axial locations in the spatial ODT formulation,}
    \item \hl{query a parameter from the input file,}
    \item \hl{return the stoichiometric mixture fraction for combustion/mixing problems, and}
    \item \hl{compute the domain bounds.}
\end{itemize}
%
\hl{In addition, a few functions are provided for doing interpolation/extrapolation, and computing probability denisity functions (PDFs), and weighted PDFs.
Many of these functions take an argument that is a dictionary of case-specific information, such as the case name and paths for key directories. This dictionary is set in the post-processing driver script based only on the user-specified case name.
}

@@

Special thanks to Alan R. Kerstein for his significant contributions to model development. Additional thanks to Heiko Schmidt, Juan Medina, and Marten Klein of Brandenburg University of Technology Cottbus-Senftenberg, Michael Oevermann and Marco Fistler of Chalmers University of Technology, and John Hewson of Sandia National Laboratories for code contributions, and insightful conversations.
